\bfseries A simple momentum-transport model for sailing

### 2021-07-05 paper/main.tex
lift, and references

\title{\bfseries%
A simple, anisotropic ram-pressure model for sailing}
\author{DWH, MK, others?}
\date{June 2021}
\begin{document}
\maketitle

@@

HOGG: Stuff about Bernoulli and flying and aerofoils that turned out to be wrong; a motivation to reconsider sailing too.

@@

HOGG: Who is our audience? People interested in simple mechanics.
We eschew real fluid dynamics; we over-simplify.
This is possible because sailing is, in fact, very simple.
We are different from the prior literature (including \cite{symmetry, explained}) because we are giving an executable model that can be played with.
This is a sailing sandbox.

@@

\section{Why ram-pressure forces? Why planar sails?}\label{sec:ram}

>>>>

\title{\bfseries%
A simple momentum-transport model for sailing}
\author{DWH, MK, others?}
\date{June 2021}
\begin{document}
\maketitle

@@

HOGG: Stuff about Bernoulli and flying and aerofoils that turned out to be wrong (see, for one of many, many examples, \cite{lift}).
This is something of a motivation to reconsider sailing too.
Note that some books (especially \cite{sails}) get the lift from the sail and keel correct: It has to involve changing the direction of flow!

@@

HOGG: Who is our audience? People interested in simple mechanics.
We eschew real fluid dynamics; we over-simplify.
This is possible because sailing is, in fact, very simple.
We are different from the prior literature (including \cite{symmetry, explained, sails}) because we are giving an executable model that can be played with.
This is a sailing sandbox.
The only prior work we know that does precisely this is \cite{tao}.

@@

\section{Why ram-pressure forces?}\label{sec:ram}
